A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Remove code listing of example program, unnecessary to repeat the code.

The \lstinline!remote! function takes an arbitrary function, provided that all
its arguments as well as its return value are serializable through the
\lstinline!Serialize! type class, and produces a typed identifier which
may be used to refer to the remote function. In this example, the type of
\lstinline!greetings! is \lstinline!Remote (String -> Server ())!,
indicating that the identifier refers
to a remote function with a single \lstinline!String! argument and no return
value. Remote functions all live in the \lstinline!Server! monad.
This part of the program is executed on both the server and the client, albeit
with slightly different side effects, as described in section \ref{sec:impl}.

@@

Figure \ref{lst:hello-server} gives the code of this example in its entirety.

\begin{listingfloat}
\begin{code}
import Haste.App

helloServer :: String -> Server ()
helloServer name =
  liftIO $ putStrLn (name ++ " says hello!")

main :: App Done
main = do
  greetings <- remote helloServer

  runClient $ do
    name <- prompt "Hi there, what is your name?"
    onServer (greetings <.> name)
\end{code}
\caption{A seamless programming model: Hello Server}
\label{lst:hello-server}
\end{listingfloat}

>>>>

The \lstinline!remote! function takes an arbitrary function, provided that all
its arguments as well as its return value are serializable through the
\lstinline!Serialize! type class, and produces a typed identifier which
may be used to refer to the remote function. In this example, the type of
\lstinline!greetings! is \lstinline!Remote (String -> Server ())!,
indicating that the identifier refers
to a remote function with a single \lstinline!String! argument and no return
value. Remote functions all live in the \lstinline!Server! monad.
The part of the program contained within the \lstinline!App! monad is executed
on both the server and the client, albeit with slightly different side effects,
as described in section \ref{sec:impl}.

@@
